Setting up Data

### 2020-04-21 doc/Results_v2.rmd
better job at removing adj_nMLH1 variables

#MLH1_data_setup_2.24.20.RData
load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_2.24.20.RData")

#load(file = "C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.31.20.RData")

#2.2.20
#load(file="C:/Users/April/Documents/MLH1repo/data/CleanBivData_1.27.20.RData")
#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/CleanBivData_1.27.20.RData")

@@

#What are the main DFs for this code chunk
#AP_mouse_table_w.Ages   <- used to remove males which are too old (includes outgroups) 
#DF.HetC.MixedModel   <- only Mmusculus
#DF.HetC.MixedModel.HQ <- only mice of certain age, Q5 excluded

#variance is still chr
#AP_mouse_table_w.Ages$var <- as.numeric(AP_mouse_table_w.Ages$var)

#use the merged DF to filter by age 
#AP_mouse_table_w.Ages$strain <- AP_mouse_table_w.Ages$strain.x
#AP_mouse_table_w.Ages$sex <- AP_mouse_table_w.Ages$sex.x
#AP_mouse_table_w.Ages$subsp <- AP_mouse_table_w.Ages$subsp.x
#main file, make everything unordered factors
#AP_mouse_table_w.Ages <- add_species(AP_mouse_table_w.Ages)

@@

#REMOVE EXTRA STRAINS
#DF.HetC.MixedModel <- DF.HetC.MixedModel[DF.HetC.MixedModel$subsp != "Cast",]
#remove musc strains
#DF.HetC.MixedModel <- DF.HetC.MixedModel[DF.HetC.MixedModel$strain != "AST",]
#DF.HetC.MixedModel <- DF.HetC.MixedModel[DF.HetC.MixedModel$strain != "TOM",]
#remove PERC, MOLF, CZECH, (no females)
#DF.HetC.MixedModel <- DF.HetC.MixedModel[DF.HetC.MixedModel$strain != "CZECH",]
#DF.HetC.MixedModel <- DF.HetC.MixedModel[DF.HetC.MixedModel$strain != "PERC",]

#DF.HetC.MixedModel <- droplevels(DF.HetC.MixedModel)#remove levels not used

#AP_mouse_table excluide Qual5 cells
DF.HetC.MixedModel.HQ <- AP_mouse_table.MLH1_HQ

DF.HetC.MixedModel.HQ <- add_species(DF.HetC.MixedModel.HQ)

>>>>

load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_4.21.20.RData")
#load(file = "C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.31.20.RData")
#2.2.20
#load(file="C:/Users/April/Documents/MLH1repo/data/CleanBivData_1.27.20.RData")
#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/CleanBivData_1.27.20.RData")

@@

@@

#AP_mouse_table excluide Qual5 cells
DF.HetC.MixedModel.HQ <- AP_mouse_table.MLH1_HQ
DF.HetC.MixedModel.HQ <- add_species(DF.HetC.MixedModel.HQ)

### 2020-04-21 src/Result_Setup.Rmd
better job at removing adj_nMLH1 variables

#MLH1_data_setup_2.24.20.RData
load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_2.24.20.RData")

#load(file = "C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.31.20.RData")

>>>>

load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_4.21.20.RData")
#load(file = "~./MLH1repo/data/MLH1/MLH1_data_setup_2.24.20.RData")
#load(file = "C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.31.20.RData")

### 2020-04-21 src/SetupData.Rmd
better job at removing adj_nMLH1 variables

                        Nmice = length(unique(mouse)),
                        Ncells  = length(adj_nMLH1.foci),
                        mean_co = as.numeric(format(round(  mean(adj_nMLH1.foci), 3 ), nsmall=3) ),
                        cV = cv(adj_nMLH1.foci),
                        var = as.numeric(format(round(   var(adj_nMLH1.foci),3), nsmall=3)),
                        sd   = round(sd(adj_nMLH1.foci), 3),
                        se   = round(sd / sqrt(Ncells), 3)
)

@@

AP_mouse_table.MLH1_HQ <- ddply(MLH1_data[MLH1_data$quality < 5,], c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(nMLH1.foci),
                        mean_co = as.numeric(format(round(  mean(nMLH1.foci, na.rm=TRUE), 3 ), nsmall=3) ),
                        cV = cv(adj_nMLH1.foci, na.rm=TRUE),

@@

                        Nmice = length(unique(mouse)),
                        Ncells  = length(adj_nMLH1.foci),
                        mean_co = as.numeric(format(round(  mean(adj_nMLH1.foci), 3 ), nsmall=3) ),
                        cV = cv(adj_nMLH1.foci),
                        var = as.numeric(format(round(   var(adj_nMLH1.foci),3), nsmall=3)),
                        sd   = round(sd(adj_nMLH1.foci), 3),
                        se   = round(sd / sqrt(Ncells), 3)
                        #quality?
)

>>>>

                        Nmice = length(unique(mouse)),
                        Ncells  = length(nMLH1.foci),
                        mean_co = as.numeric(format(round(  mean(nMLH1.foci), 3 ), nsmall=3) ),
                        cV = cv(nMLH1.foci),
                        var = as.numeric(format(round(   var(nMLH1.foci),3), nsmall=3)),
                        sd   = round(sd(nMLH1.foci), 3),
                        se   = round(sd / sqrt(Ncells), 3)
)

@@

AP_mouse_table.MLH1_HQ <- ddply(MLH1_data[MLH1_data$quality < 5,], c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(nMLH1.foci),
                        mean_co = as.numeric(format(round(  mean(nMLH1.foci, na.rm=TRUE), 3 ), nsmall=3) ),
                        cV = cv(nMLH1.foci, na.rm=TRUE),

@@

                        Nmice = length(unique(mouse)),
                        Ncells  = length(nMLH1.foci),
                        mean_co = as.numeric(format(round(  mean(nMLH1.foci), 3 ), nsmall=3) ),
                        cV = cv(nMLH1.foci),
                        var = as.numeric(format(round(   var(nMLH1.foci),3), nsmall=3)),
                        sd   = round(sd(nMLH1.foci), 3),
                        se   = round(sd / sqrt(Ncells), 3)
                        #quality?
)
